---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pathways

## Overview

This package contains functions to process data for pathways. It contains functions to generate transition file and to transition from model indicator names to default indicator names. It also contains other functions to process data initially like delete rows, fill cells, find text etc.

## Installation

You can install pathways from github using devtools.

If you are using devtools for the first time you will need to install it using:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
```

You can install pathways using:

```{r py-installation, eval = FALSE}
library("devtools")
install_github("rexon1992/pathways")
```

## Example

This is an example which shows how the transition function in the package can be used:

```{r}
library(pathways)
transition("example_inputs/CPM_raw_data","example_inputs/CMP_TR",notes = 1,"example_inputs/ind_list_production.xlsx")
```

This command will write a datafile into the directory called CPM_raw_data_UL.csv with the model indicator names replaced by default indicator names and as the notes attribute is set to 1 it will also write a file called CPM_raw_data_notes.csv into the directory which can be used to add conversion factors and notes for the indicators.
